---
title: "Layouts"
author: Brandon Moretz
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Layouts}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Format Objects

```{r setup}
library(dyn.log)

# set logging config with tweaks for kitr output
set_log_configuration(file_name = system.file("knitr.yaml", 
                                              package = "dyn.log"))
```

```{r, comment="", results="asis", echo=F}
options(crayon.enabled=TRUE)
knitr::opts_chunk$set(collapse = TRUE,
                      fig.path = "man/figures/FORMAT-",
                      comment = "")
old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
```

## Overview

Log **Layouts** are the mechanism that ties everything in the package together with a composition based design. A log layout is essentially a container for formats, which defines exactly how the log message will get rendered. Layouts also have additional metadata attributes which allow for overrides to the default format *separators*, *spacing*, etc., as well as mechanism for associating a particular log layout with a type of R6 class.

### Defaults

There are two basic layouts that come with the standard configuration (*default.yaml*) bundled with the package, **default** and **log_level**.

```yaml
layouts:
- association: default
  seperator: !expr as.character(' ')
  new_line: !expr as.character('\n')
  formats: new_fmt_log_level(),
           new_fmt_timestamp(crayon::silver$italic),
           new_fmt_log_msg()
- association: level_msg
  seperator: !expr as.character(' ')
  new_line: !expr as.character('\n')
  formats: new_fmt_log_level(),
           new_fmt_log_msg()

```

```{r}

```

