---
title: "Layouts"
author: Brandon Moretz
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Layouts}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Format Objects

```{r setup}
library(dyn.log)

# set logging config with tweaks for kitr output
set_log_configuration(file_name = system.file("knitr.yaml", 
                                              package = "dyn.log"))
```

```{r, comment="", results="asis", echo=F}
options(crayon.enabled=TRUE)
knitr::opts_chunk$set(collapse = TRUE,
                      fig.path = "man/figures/FORMAT-",
                      comment = "")
old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
```

## Overview

Format objects are the driver of customization in log rendering. Log layouts were developed with the [composition](https://en.wikipedia.org/wiki/Composite_pattern) design pattern in mind; a log layout is simply a series of formats that get evaluated with their associated context to form a log message.

All formats derive from the **fmt_layout** base type and have a couple of generics associated with them, specifically: **style** and **value**. The **fmt_layout** is meant to be an [abstract](https://en.wikipedia.org/wiki/Abstract_type) base type; by driving from it the logging framework can make some assumptions about how to treat a format object.
